RNA-seq from 4 cell populations

### 2021-08-02 deconvolution/fans4/molec_profiling.Rmd
bug fix

# Gene set analysis
```{r zenith.celltype, cache=FALSE}
knitr::knit_exit()

>>>>

# Gene set analysis
```{r zenith.celltype, cache=FALSE}

geneSets_GO = get_GeneOntology()

# Map from Ensembl genes in geneSets_GO to 
# Ensembl names from RNA-seq data 
index = ids2indices( recodeToList(geneSets_GO), rownames(fitBasic))

idxGO = index[sapply(index, length) > 20]

df_CT_zenith = lapply( colnames(coef(fitBasic))[1:2], function(key){
  res = zenith( fitBasic, coef = key, index = idxGO)
  data.table(Geneset = rownames(res), res, coef = key)
})
df_CT_zenith = do.call(rbind, df_CT_zenith)

df_CT_zenith[coef == 'GABA_vs_Olig',]
